Evaluating the leaf photosynthetic rates?

### 2016-07-17 Main.Rmd
書き進め。Fig.1 (分配の模式図) を作成。

HID_raw <-
  fread("~/Dropbox/R/spectrum/HID.csv", skip = 13)

HIDs <-
  HID_raw %>%
  setnames(., c("wavelength", paste0("ID", 1:(dim(HID_raw)[2] - 1)))) %>%
  select(1, HPS_ = 12, MH_ = 21)

@@

SPDs <-
  # left_join(HIDs, Sun, by = "wavelength") %>%
  Sun %>%
  SPDnorm(from = 350, to = 750, integratedPFD = 100) %>%
  select(-Absorptance) %>%
  gather(variable, value, -wavelength) %>%
  bind_rows(., HPS_Ocean) %>%
  bind_rows(., MH_Ocean) %>%
  filter(between(wavelength, 350, 800)) %>%
  ggplot(aes(x = wavelength, y = value, group = variable, col = variable)) +
  theme_bw2(legend = "right") +
  geom_line() +
  xlab("Wavelength [nm]") + ylab(u_SPFD("Spectral photon flux density"))

@@

Abbreviations
ML
Pg
Pn
ETR
SPD
PPFD

@@

  The photosynthetic rate is one of the most important and commonly reported phenotype for the plant sciences.
  Considering the importance of the photosynthetic rate, the effects on the rates were measured, evaluated, and compared among the leaves cultivated under different conditions, typically control and treatment.
  Based on the measured rates, the impacts of the treatments are discussed.
  Thus, the reliable measurements must be made prior to the evaluation.

@@

  Light energy absorbed by a leaf drives photosynthetic electron transport, and thereby the photosynthetic carbon **fixation**.
  In higher plants, the photosynthetic electron transport chain is anchored by photochemical reactions that occur at two types of photosystems, PSII and PSI.
  The electron transports are powered by photon energy transferred to the respective photosystems, thus enabling electron transfer against the redox potential (called the Z scheme).
  Because photosynthetic electron transport reactions occur in series, the electron transport rate (ETR) is limited by the slowest step.
  Therefore, when the excess energy is distributed to PSII, the energy distribution to PSI limits the ETR and light use efficiency (i.e. photochemical quantum yield) of PSII is lowered (Fig. 1A) and *vice versa* (Fig. 1B).
  Note that the balanced distribution should not be 50-50 basis because the rate-limiting photosystem does not always perform the photochemical reaction at a quantum yield of a 100%.
  Even in a dark adapted helthy leaf, the yield of PSII cannot exceed 0.84 (i.e. chl fluorescence parameter *F*~v~/*F*~m~).
  Although there is no clear consensus, the maximum yield of PSI seems to be greater than that of PSII.
  A little bit greater distribution to PSII should be required to make maximum use of the absorbed photons.
  Gentyに触れるか？

  **AEFに言及**

  **The imbalance between the photosystems ** can be caused by the SPD of light.
  These photosystems represent different light absorption spectral distributions due to the difference in the compositions of binding pigments, mainly chlorophyll (chl) *a* and *b*.
  Within the chlorophyll (chl) absorption band (approximately 350--750 nm), longer wavelengths of light (> 680--690 nm) are estimated to be preferentially absorbed by PSI, and PSI is drastically overexcited [@Evans1986PhotoPhoto; @Evans1987FPB; @Wientjes_et_al2013BBA; @Laisk_et_al2014BBA].
  Such an umbalanced distribution was caused by the facts that only chl *a* can absorb light within the longer waveband and that PSI contains a greater amount of chl *a* than PSII.
  Monochromatic light at shorter wavelengths (< 680--690 nm) is estimated to be preferentially absorbed by PSII (especially in the wavebands near 470 and 650 nm corresponding to the absorption peaks of chl *b*---abundant in PSII), or evenly absorbed by both PSs [@Evans1986PhotoPhoto; @Evans1987FPB; @Wientjes_et_al2013BBA; @Laisk_et_al2014BBA].
  These wavelength dependency of the distribution balance is a determinant of EED under a given SPD of light.
  以降はPSIIとPSI-lightを使う。相対的なものだ。
  In this study, the terms ‘PSII-light’ and ‘PSI-light’ are used only in a relative context.
  That is, we state which should be more PSII-biased when referring to two (or more) SPDs.
  Thus, light with a given SPD can be categorized as either PSII or PSI-light according to whether the excitation energy is preferentially distributed to PSII or PSI, respectively.

  Apparently, the distribution is affected by the stoichiometry of the membrane composition, vulneerable to the SPD of light during the leaf growth [@].
  **In the short term, the distribution of excitation energy is adjusted by the dynamic allocation of the light-harvesting antenna complex of PSII (LHCII) to PSI [state transition; for a review, see @Goldschmidt-Clermont_Bassi2015CurOpin].**
  **When state transitions are insufficient to counterbalance the uneven distribution of excitation energy, a long-term acclimation response occurs [@Dietzel_et_al2008FJ].**
  Under PSII-light, the relative amount of the reaction center complex of PSII to that of PSI in leaves decreases.
  Conversely, under PSI-light, the relative amount increases to achieve a balance [@Chow_et_al1990PCE; @Chow_et_al1990PNAS; @Smith_et_al1993PCE; @Walters_Horton1994Planta; @Walters_Horton1995bPlanta; @Pfannschmidt_et_al1999Nature; @Wagner_et_al2008Planta; @Hogewoning_et_al2012PC].
  These reactions are believed to be induced so that balance the *excitation balance*.
  簡単にいうと、leaves grown under PSII-light tend to distribute the photons to PSI and leaves grown under PSI-light tend to distribute the photons to PSII.

  Expected interactions have been reported in several studies [@].
  In their study on *Pisum sativum*, @Chow_et_al1990PNAS reported that adjustments in PS stoichiometry allowed the plant to maintain a high quantum efficiency of photosynthesis.
  In that study, pea plants were grown under **cool-white fluorescent lamps with yellow Plexglas and incandescent bulbs with red Plexglas** (PSII- and PSI-light, respectively) and the photosynthetic quantum yield of O~2~ evolution---O~2~ evolution rate per absorbed photons by leaf---was measured under PSII- and PSI-light.
  When measured under PSII-light, the yield was higher in PSII-light-grown leaves; when measured under PSI-light, the yield was higher in PSI-light-grown leaves.
  A similar trend was observed in other studies on *Arabidopsis thaliana* [@Walters_Horton1995aPlanta] and *Cucumis sativus* [@Hogewoning_et_al2012PC; @Murakami_et_al2016PhysiolPlant] (Table. 1).
  **@Walters_Horton1995aPlanta used halogen lamp and filters **
  **@Hogewoning_et_al2012PC used an artificial sunlight [@Hogewoning_et_al2010aJXB] and blue LED light as PSII-light and an artificial shadelight as PSI-light.**
  **@Murakami_et_al2016PhysiolPlant compared the photosynthetic rates of leaves grown under white LED light without and with supplemental far-red LED light (W- and WFR-leaves) using blue-red LED light source sunlight-like SPD of light.**
  **The photosynthetic rate of W-leaves was greater than that of WFR-leaves under BR LED light (i.e. PSII-light), while the rates were comparable between the leaves, or slightly greater in the WFR-leaves, under sunlight (i.e. PSI-light).**
  These studies indicated that comparisons of leaf photosynthetic rates between plants grown under different SPDs of light can be biased depending on the SPD of measuring light (ML).
  @Walters2005JXB pointed out.

@@

  Apparently, measuring the photosynthetic rates with plural levels of SPDs costs  
  また太陽光あるいは葉の透過光だったりと複雑な分光分布を再現するのは現実には難しい。
  To omit the evaluation of the multi-levels of the SPDs in the descriptive evaluation of the leaf photosynthesis, the determinant parameters are required to be defined and to be quantified.
  これらを避けるためには、交絡因子の数値化が必要であろう。

@@

```{r FigETR, fig.cap = CapSPD}
ETRs
```

```{r Fig, fig.cap = CapSPD}
FigStructure
```

@@

```{r FigInteract, fig.cap = CapInteract}
InteractionView
```
# References

>>>>

# HID_raw <-
#   fread("~/Dropbox/R/spectrum/HID.csv", skip = 13)
# 
# HIDs <-
#   HID_raw %>%
#   setnames(., c("wavelength", paste0("ID", 1:(dim(HID_raw)[2] - 1)))) %>%
#   select(1, HPS_ = 12, MH_ = 21)
FL_Ocean_raw <-
  fread("~/Dropbox/materials/SPD_FL.csv") %>%
  transmute(wavelength = `Wavelength[nm]`, value = FL) %>%
  na.omit

FL_Ocean_PFD <-
  smooth.spline(FL_Ocean_raw$wavelength, FL_Ocean_raw$value) %>%
    predict(., seq(PFD_integrate_min, PFD_integrate_max)) %>%
    .$y %>%
  sum

FL_Ocean <-
  FL_Ocean_raw %>%
  mutate(value = value * 100 / FL_Ocean_PFD, variable = "FL")

@@

SPDs <-
  # left_join(HIDs, Sun, by = "wavelength") %>%
  Sun %>%
  SPDnorm(from = 350, to = 750, integratedPFD = 100) %>%
  select(-Absorptance) %>%
  gather(variable, value, -wavelength) %>%
  bind_rows(., FL_Ocean) %>%
  bind_rows(., HPS_Ocean) %>%
  bind_rows(., MH_Ocean) %>%
  filter(between(wavelength, 350, 800)) %>%
  ggplot(aes(x = wavelength, y = value, group = variable, col = variable)) +
  theme_bw2(legend = "right") +
  geom_line() +
  xlab("Wavelength [nm]") + ylab(u_SPFD("Spectral photon flux density"))

@@

**Abbreviations**
ETR: 
ML: measuring light
Pn: 
PPFD: photosynthetic photon flux density
SPD: spectral PFD distribution

@@

  The net photosynthetic rate is one of the most important and commonly reported phenotype for the plant sciences.
  Considering the importance of the photosynthetic rate, the effects on the rates were measured, evaluated, and compared among the leaves cultivated under different conditions, typically control and treatment.
  Based on the measured rates, the impacts of the treatments are discussed.
  Thus, the reliable measurements must be made prior to the evaluation.

@@

  The knowledge about the photosynthetic electron transport is required to understand the mechanism of the interaction.
  Light energy absorbed by a leaf drives the electron transport, and thereby the photosynthetic O~2~ evolution and CO~2~ uptake.
  In higher plants, the photosynthetic electron transport chain is anchored by photochemical reactions that occur at two types of photosystems, PSII and PSI.
  The electron transports are powered by photon energy transferred to the respective photosystems, thus enabling electron transfer against the redox potential (called the Z scheme).
  Because photosynthetic electron transport reactions occur in series, the electron transport rate (ETR) is limited by the slowest step (Fig. 1).
  When the excess energy is distributed to PSII under the imbalanced energy distribution, the energy distribution to PSI limits the ETR and the photochemical quantum yield of PSII is lowered (Fig. 1A).
  When the excess energy is distributed to PSI, the energy distribution to PSII limits the ETR and the yield of PSI is lowered (Fig. 1D).
  In both cases, a part of absorbed photons is dissipated as heat and fluorescence, and thus the entire photosynthetic quantum yield---the bulk ETR per absorbed photon---becomes smaller.

  Note that the balanced distribution should not be 50-50 basis because the rate-limiting photosystem does not always perform the photochemical reaction at a quantum yield of a 100%.
  Even in a dark adapted helthy leaf, the yield of PSII cannot exceed 0.84 (i.e. chl fluorescence parameter *F*~v~/*F*~m~).
  Although there is no clear consensus, the maximum yield of PSI seems to be greater than that of PSII.
  A little bit greater distribution to PSII should be required to make maximum use of the absorbed photons.
  Gentyに触れるか？
  **AEFに言及**

  **The imbalance between the photosystems ** can be caused by the SPD of light.

  PSII and PSI represent different light absorption spectral distributions due to the difference in the compositions of binding pigments, mainly chlorophyll (chl) *a* and *b*.
  Within the chlorophyll (chl) absorption band (approximately 350--750 nm), longer wavelengths of light (> 680--690 nm) are estimated to be preferentially absorbed by PSI, and PSI is drastically overexcited [@Evans1986PhotoPhoto; @Evans1987FPB; @Wientjes_et_al2013BBA; @Laisk_et_al2014BBA].
  Such an umbalanced distribution was caused by the facts that only chl *a* can absorb light within the longer waveband and that PSI contains a greater amount of chl *a* than PSII.
  Monochromatic light at shorter wavelengths (< 680--690 nm) is estimated to be preferentially absorbed by PSII (especially in the wavebands near 470 and 650 nm corresponding to the absorption peaks of chl *b*---abundant in PSII), or evenly absorbed by both PSs [@Evans1986PhotoPhoto; @Evans1987FPB; @Wientjes_et_al2013BBA; @Laisk_et_al2014BBA].
  These wavelength dependency of the distribution balance is a determinant of EED under a given SPD of light.
  この分野の研究では, light with a given SPD is categorized as either PSII or PSI-light according to whether the excitation energy is preferentially distributed to PSII or PSI, respectively.
  この判断はおおむね主観で決められている。FRが増えればPSI-light。

  Apparently, the distribution is affected by the stoichiometry of the membrane composition, vulnerable to the SPD of light during the leaf growth [@].
  **In the short term, the distribution of excitation energy is adjusted by the dynamic allocation of the light-harvesting antenna complex of PSII (LHCII) to PSI [state transition; for a review, see @Goldschmidt-Clermont_Bassi2015CurOpin].**
  **When state transitions are insufficient to counterbalance the uneven distribution of excitation energy, a long-term acclimation response occurs [@Dietzel_et_al2008FJ].**
  Under PSII-light, the relative amount of the reaction center complex of PSII to that of PSI in leaves decreases.
  Conversely, under PSI-light, the relative amount increases to achieve a balance [@Chow_et_al1990PCE; @Chow_et_al1990PNAS; @Smith_et_al1993PCE; @Walters_Horton1994Planta; @Walters_Horton1995bPlanta; @Pfannschmidt_et_al1999Nature; @Wagner_et_al2008Planta; @Hogewoning_et_al2012PC].
  These reactions are believed to be induced so that balance the *excitation balance*.

  The terms ‘PSII-light’ and ‘PSI-light’ are used only in a relative context.
  For instance, a SPD of light, which is in good balance for PSII-leaves, can overexcite PSII in PSI-leaves (Fig. 1AB).

  簡単にいうと、leaves grown under PSII-light tend to distribute the photons to PSI and leaves grown under PSI-light tend to distribute the photons to PSII. 
  Expected interactions have been reported in several studies [@].
  In their study on *Pisum sativum*, @Chow_et_al1990PNAS reported that adjustments in PS stoichiometry allowed the plant to maintain a high quantum efficiency of photosynthesis.
  In that study, pea plants were grown under **cool-white fluorescent lamps with yellow Plexglas and incandescent bulbs with red Plexglas** (PSII- and PSI-light, respectively) and the photosynthetic quantum yield of O~2~ evolution---O~2~ evolution rate per absorbed photons by leaf---was measured under PSII- and PSI-light.
  When measured under PSII-light, the yield was higher in PSII-light-grown leaves; when measured under PSI-light, the yield was higher in PSI-light-grown leaves.
  A similar trend was observed in other studies on *Arabidopsis thaliana* [@Walters_Horton1995aPlanta] and *Cucumis sativus* [@Hogewoning_et_al2012PC; @Murakami_et_al2016PhysiolPlant] (Table. 1).
  **@Walters_Horton1995aPlanta used halogen lamp and filters **
  **@Hogewoning_et_al2012PC used an artificial sunlight [@Hogewoning_et_al2010aJXB] and blue LED light as PSII-light and an artificial shadelight as PSI-light.**
  **@Murakami_et_al2016PhysiolPlant compared the photosynthetic rates of leaves grown under white LED light without and with supplemental far-red LED light (W- and WFR-leaves) using blue-red LED light source sunlight-like SPD of light.**
  **The photosynthetic rate of W-leaves was greater than that of WFR-leaves under BR LED light (i.e. PSII-light), while the rates were comparable between the leaves, or slightly greater in the WFR-leaves, under sunlight (i.e. PSI-light).**
  These studies indicated that comparisons of leaf photosynthetic rates between plants grown under different SPDs of light can be biased depending on the SPD of measuring light (ML).
  @Walters2005JXB pointed out.

@@

  Apparently, measuring the photosynthetic rates under multilevels of SPDs costs much more time, resource, and labor.
  また太陽光あるいは葉の透過光だったりと複雑な分光分布を再現するのは現実には難しい。
  To omit the evaluation of the multi-levels of the SPDs in the descriptive evaluation of the leaf photosynthesis, the determinant parameters are required to be defined and to be quantified.
  これらを避けるためには、交絡因子の数値化が必要であろう。

@@

![FigETR](FigETR.png)

```{r Fig, eval = F, fig.cap = CapSPD}
FigStructure
```

@@

```{r FigInteract, fifig.cap = CapInteract}
InteractionView
```
# References
